---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jasmines

<!-- badges: start -->
<!-- badges: end -->

The jasmines package is what I use to make a lot of my generative artwork with R. Internally it relies heavily on the [ambient](https://github.com/thomasp85/ambient) package, and you may need to install the developer version of ambient to make it work:

``` r
# install.packages("remotes")
# remotes::install_github("thomasp85/ambient")
remotes::install_github("djnavarro/jasmines")
```

Functions in the jasmines package are designed to work with the dplyr pipe, so you will likely want to have dplyr loaded:

```{r packageload, message=FALSE, warning=FALSE}
library(dplyr)
library(jasmines)
```

## Example 1

A typical jasmines pipeline looks like this:

```{r example1}
use_seed(1) %>%
  entity_circle(grain = 1000) %>%
  unfold_tempest(iterations = 10) %>%
  style_ribbon(background = "wheat")
```

The `use_seed()` function is a convenience function that sets the random number generator seed, and stores that value for later use. The seed is then piped to an `entity_` function (or a `scene_` function) that creates the initial object that will be operated upon. In this case this initial object is a circle of diameter 2 rendered using 1000 points. This is then passed to an `unfold_` function, that iteratively applies some operation (in this case the "warp") operation for some number of steps (in this case 100). The object is converted to a ggplot2 image using one of the `style_` functions. In this and most cases the `style_ribbon()` is used and has several customisable finctions. 

## Example 2

```{r example2}
use_seed(1) %>%
  entity_circle(grain = 1000, size = 2) %>%
  unfold_warp(iterations = 100) %>%
  style_ribbon(palette = "rainbow")
```

## Example 3

An example where the initial object is created with `entity_heart()`, the unfolding performed by `unfold_slice()` and the styling is more elaborate.

```{r example3}
use_seed(1) %>%
  entity_heart(grain = 1000) %>%
  unfold_slice(iterations = 10) %>%
  style_ribbon(
    palette = "base", 
    colour = "ind", 
    background = "mistyrose"
  ) %>%
  style_overlay(border = "white")
```

## Example 4

It is possible to create "scenes" comprised of multiple entities as the initial starting point, apply multiple unfolding operations, and modify the way transparency and colouring is done.

```{r example4}
use_seed(1) %>%
  scene_discs(
    rings = 3, points = 5000, size = 5
  ) %>%
  mutate(ind = 1:n()) %>%
  unfold_warp(
    iterations = 1,
    scale = .5, 
    output = "layer" 
  ) %>%
  unfold_tempest(
    iterations = 20,
    scale = .01
  ) %>%
  style_ribbon(
    palette = palette_named("vik"),
    colour = "ind",
    alpha = c(.1,.1),
    background = "oldlace"
  )
```

To save the image to a file, the pipeline can include an additional step that uses the `export_image()` function. 
